---
title: GRR 分析報告範例
author: R package build
date: '2021-07-07'
slug: grr-report-example
categories:
  - GRR
tags:
  - GRR
Description: 'An example of GRR reporting by Rmarkdown'
---

```{r global_options, include=FALSE} 
knitr::opts_chunk$set(dev='png',echo=FALSE, warning=FALSE, message=FALSE) 
```


```{r, include=FALSE, cache=TRUE}
options(knitr.kable.NA = '')
# Load libraries and raw data
library(formattable)
library(kableExtra)
library(knitr)
library(lubridate)
library(scales)
library(ggplot2)
library(GGally)
library(tidyr)
library(dplyr)
library(readr)
library(tibble)
library(stringr)
library(purrr)
library(forcats)
library(plotly)
library(setGplot)
library(setPlotly)
library(spcChart)
library(qcc)
library(car)
source("../function/grr_functions.R")
source("../function/spc_functions.R")
source("../function/html_setting.R")


# parameters
df = read_csv("../data/grr_data.csv")
tolerance = 66
grr_criteria = c(0.1, 0.3)

# grr 
li_grr <- fun.grr.std(df, tolerance)
tb_grr <- li_grr$tb_grr

```

這是 GRR 分析報告的一個範例。以圖表配合解說，讓使用者更輕鬆的的解讀 GRR 測試的結果以做出更正確的判斷。

使用的工具和方法參考<a href="http://shiny.sightingdata.com/shiny/grr" target="_blank">GRR分析應用工具</a>和<a href="/post/grr_interpret" target="_blank">如何解讀 GRR 分析結果</a>。

<hr>
<!--- body section --->
## GRR summary

```{r grr_note, results= 'asis', cache=TRUE}
cat("<div class= 'listx'>")

# GRR
perSV <- tb_grr["Total R&R", "perSV"]
if (perSV <= grr_criteria[1] * 100) {
    mark <- check_mark
    note <- "The measurement system is acceptable."
} else if (perSV <= grr_criteria[2] * 100) {
    mark <- excla_mark
     note <- "The measurement system is potentially acceptable."
} else {
    mark <- cross_mark
    note <- "The measurement system is not acceptable."
}
note <- paste0("%GRR = ", round(perSV, 1), " : <br>", note)

cat("<p>", mark, note, "</p>")

# NDC
if (li_grr$ndc <5) {
    mark <- cross_mark
    note <-"The measurement system cannot well distinguish between parts."
} else {
    mark <- check_mark
    note <- "The measurement system can distinguish between parts."
}
note <- paste0("Number of distinct categories = ", li_grr$ndc, " : <br>", note)

cat("<p>", mark, note, "</p>")


# Proportion of repeatiblity to reproducibility
perRepeat <- round(tb_grr["Repeatability", "Variance"] / tb_grr["Total R&R", "Variance"] * 100, 1)
perReprod <- round(tb_grr["Reproducibility", "Variance"] / tb_grr["Total R&R", "Variance"] * 100, 1)

mark <- info_mark
note <- paste0("Repeatability contributes ", perRepeat, 
                "% of GRR variance, and reproducibility contributes ", 
                perReprod, "%.")
cat("<p>", mark, note, "</p>")

# Effect of operator
pValue_operator <- round(li_grr$aov["Operator", "Pr(>F)"], 3)
if (pValue_operator < 0.05) {
    mark <- cross_mark
    if (nrow(tb_grr) > 5) {
        varx <- tb_grr["Operator", "Variance"]
    } else {
        varx <- tb_grr["Reproducibility", "Variance"]
    }
    perOperator <- round(varx / tb_grr["Total R&R", "Variance"] * 100, 1)
    note <- paste0("Effect of operators is significant, with p-value of ANOVA = ", 
                    pValue_operator,
                   ".<br>Operator contributes ", perOperator, "% of GRR variance.")
} else {
    mark <- check_mark
    note <- "Effect of operator is not significant."
}

cat("<p>", mark, note, "</p>")

# Interaction
if (li_grr$pValue_interact < 0.05) {
    mark <- cross_mark
    perInt <- round(tb_grr["Operator:Part", "Variance"] / tb_grr["Total R&R", "Variance"] * 100, 1)
    note <- paste0("Interaction between operators and parts is significant, with p-value of ANOVA = ",
                    round(li_grr$pValue_interact, 3),
                   ".<br>Interaction contributes ", perInt, "% of GRR variance.")
} else {
    mark <- check_mark
    note <- "There is no interaction between operators and parts."
}
cat("<p>", mark, note, "</p>")

# GRR conditions
mark <- info_mark
note <- paste0("Number of operators = ", li_grr$n_operator,
                ", Number of trials = ", li_grr$n_trial,
                ", Number of parts = ",  li_grr$n_parts)
cat("<p>", mark, note, "</p>")

cat("</div>")
```


```{r, cache=TRUE}
# create GRR table
colnames = c("Variance", "Std. Dev.", "Study Var.", "% Study Var.", 
             "% Contribution")
if (! is.null(tolerance)) {
    colnames = c(colnames, "% Tolerance")
}

tbl <- kable(tb_grr, col.names = colnames, digits = c(3, 3, 3, 1, 1, 1),
      caption = "GRR table") %>%
    kable_styling(bootstrap_options = c("hover"),
                full_width = F,
                font_size = 14,
                position = "left") %>%
    add_indent(2:3) %>%
    column_spec(c(1,5), bold = T) %>%
    row_spec(2:3, color = "grey")
if (nrow(tb_grr) > 5) {
    tbl <- tbl %>%
        add_indent(4:5) %>%
        add_indent(4:5) %>%
        row_spec(4:5, color = "grey")
}

```

```{r grr_table, results= 'asis', dpi=72, fig.width= 10, fig.asp = 0.618, cache=TRUE}
# show compoent plot
li_grr$p_comp

# show grr table
tbl 
```

<hr>

## X&#772;-R chart

```{r Xbar-R_analysis, include= FALSE, cache=TRUE}
df_xbar <- li_grr$li_spc$df_xbar
total_points <-  nrow(df_xbar)
xbar_ooc_rate <- nrow(df_xbar[df_xbar$label != "normal",]) / total_points
if (xbar_ooc_rate < 0.5) {
    mark1 <- cross_mark
    note1 <- "That means the parts variation is difficult to detect by the measurement system."
} else if (xbar_ooc_rate < 0.8) {
    mark1 <- excla_mark
    note1 <- "That means the measurement system can but not well detect the parts variation."
} else {
    mark1 <- check_mark
    note1 <- "That means the parts variation is easy to detect by the measurement system."
}

df_r <- li_grr$li_spc$df_r
r_normal_rate <- nrow(df_r[df_r$label == "normal", ]) / total_points
if (r_normal_rate < 0.75) {
    mark2 <- cross_mark
    note2 <- "There is no consistency to the measurement system."
} else if (r_normal_rate < 0.95) {
    mark2 <- excla_mark
    note2 <- "The measurement system potentially has decent consistency."
} else {
    mark2 <- check_mark
    note2 <- "The measurement system has good consistency."
}
```

<div class= 'listx'>
`r mark1` X&#772; chart of this GRR test has `r round(xbar_ooc_rate * 100)`% of data points out of control. `r note1`

`r mark2` R chart of this GRR test has `r round(r_normal_rate * 100)`% data points inside control limits. `r note2`
</div>

```{r x_r_chart, results='asis', dpi=72, fig.width= 10, fig.asp = 0.618, cache=TRUE}
li_grr$li_spc$p
```

<hr>

## Measurement by operators

```{r operator, results='asis', cache=TRUE}
cat("<div class= 'listx'>")

# Effect of operator
pValue_operator <- round(li_grr$aov["Operator", "Pr(>F)"], 3)
if (pValue_operator < 0.05) {
     mark <- cross_mark
    note <- "No"
} else {
    mark <- check_mark
    note <- "Yes"
}
note <- paste0("Operators measuring the parts similiarly: ", note,
               ".<br>P-value of ANOVA (comparing mean) = ", pValue_operator, ".")
cat("<p>", mark, note, "</p>")

# Equal variation across operators
operator_varTest_pValue <- round(li_grr$operator_varTest_pValue, 3)
if (operator_varTest_pValue < 0.05) {
    mark <- cross_mark
    note <- "No"
} else {
    mark <- check_mark
    note <- "Yes"
}
note <- paste0("Operators' measurement have the same variation: ", note, 
               ".<br>P-value of Levene's test (comparing variance) = ", 
               operator_varTest_pValue, ".")
cat("<p>", mark, note, "</p>")

cat("</div>")

# plot
li_grr$p_oper
```

<hr>

## Interaction of operator by part
```{r interaction, results='asis', cache=TRUE}
cat("<div class= 'listx'>")
if (li_grr$pValue_interact < 0.05) {
    mark <- cross_mark
    note <- "No"
} else {
    mark <- check_mark
    note <- "Yes"
}
note <- paste0("No interaction between operators and parts: ", note, 
               ".<br>P-value of ANOVA = ", round(li_grr$pValue_interact, 3), ".")

cat("<p>", mark, note, "</p>")

cat("</div>")

# plot
li_grr$p_inter
```

<hr>

## Measurement by parts
```{r part, results= 'asis', cache=TRUE}
cat("<div class= 'listx'>")
# Equal variation across operators
part_varTest_pValue <- round(li_grr$part_varTest_pValue, 3)
if (part_varTest_pValue < 0.05) {
    mark <- cross_mark
    note <- "No"
} else {
    mark <- check_mark
    note <- "Yes"
}
note <- paste0("Parts are measured with the same variation: ", note, 
               ".<br>P-value of Levene's test (comparing variance) = ", 
               part_varTest_pValue, ".")
cat("<p>", mark, note, "</p>")

cat("</div>")

# plot
li_grr$p_part
```

<hr>

## ANOVA
```{r, results='asis', cache=TRUE}
options(knitr.kable.NA = '')
kable(li_grr$aov, digits = 3) %>%
    kable_styling(full_width = F)
```

<hr>
